
### {{ title }}

<!-- Component created on {{ date }} -->

```{r}
{{ env_id }} = readRDS("envs/{{ env_id }}.rds")

is_shiny <- identical(knitr::opts_knit$get("rmarkdown.runtime"), "shiny")
```

```{r, eval=!is_shiny}

```

```{r, eval=is_shiny}
df <- data.frame({{ env_id }}$cluster[1], {{ env_id }}$x)
#print(df)
title <- "Detected genes"
p <- plotly::plot_ly(df, y = df[[1]], x = df[[2]], type = "box", name = df[[1]])
p <- plotly::layout(p,
                    xaxis = list(title=title, showline = T),
                    yaxis = list(title="Cluster", showline = T, showticklabels = T),
                    showlegend = T
)
p
```

***

Plot description:

Sequencing is called *saturated* when generating more sequencing output from a cDNA library does not substantially increase the number of detected features in a sample. Since the number of detected features can act as a technical confounder, and thereby drive substructure in the data, it is advisable to aim for a saturated sequencing by either adding more sequencing output or decreasing the number of samples until saturation is achieved. [@zhang_one_2018] gives advise on how to choose the optimal cell number given a fixed sequencing budget


