
### {{ title }}

<!-- Component created on 2019-05-03 15:14:07 -->

```{r}
{{ env_id }} = readRDS("envs/{{ env_id }}.rds")

is_shiny <- identical(knitr::opts_knit$get("rmarkdown.runtime"), "shiny")
```

```{r, eval=!is_shiny}

x_value <- {{ env_id }}$x[[1]]
x_title <- names({{ env_id }}$x[1])

y_value <- {{ env_id }}$y[[1]]
y_title <- names({{ env_id }}$y[1])

if(!is.null({{ env_id }}$colour_by)) {
  colour_value <- {{ env_id }}$colour_by[[1]]
}

p <- plotly::plot_ly(data.frame(x_value, y_value, colour_value = I("black")),
             x = x_value,
             y = y_value,
             color = colour_value
)
p <- plotly::layout(p,
            xaxis = list(title = x_title),
            yaxis = list(title = y_title))
p

```

```{r, eval=is_shiny}

ui_list <- list()
# selection field for x
if ({{ env_id }}$x_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_x_{{ env_id }}", label = "Select data for x axis:",
              choices = names({{ env_id }}$x)))
}

# selection field for y
if ({{ env_id }}$y_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_y_{{ env_id }}", label = "Select data for y axis:",
              choices = names({{ env_id }}$y)))
}

# selection field for colour_by
if ({{ env_id }}$colour_by_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_colour_{{ env_id }}", label = "Select colouring:",
              choices = names({{ env_id }}$colour_by)))
}

fillCol(flex = c(NA, 1),
        do.call("inputPanel", ui_list),
        plotly::plotlyOutput("plot_{{ env_id }}", height = "100%")
        )

output$plot_{{ env_id }} <- plotly::renderPlotly({

  if (!{{ env_id }}$x_selection){
    x_value <- {{ env_id }}$x[[1]]
    x_title <- names({{ env_id }}$x)
  } else {
    x_value <- {{ env_id }}$x[[input$select_x_{{ env_id }}]]
    x_title <- input$select_x_{{ env_id }}
  }

  if (!{{ env_id }}$y_selection){
    y_value <- {{ env_id }}$y[[1]]
    y_title <- names({{ env_id }}$y)
  } else {
    y_value <- {{ env_id }}$y[[input$select_y_{{ env_id }}]]
    y_title <- input$select_y_{{ env_id }}
  }

  if (!{{ env_id }}$colour_by_selection){
    colour_value <- {{ env_id }}$colour_by[[1]]
  } else {
    colour_value <- {{ env_id }}$colour_by[[input$select_colour_{{ env_id }}]]
  }

  p <- plotly::plot_ly(data.frame(x_value, y_value, colour_value = I("black")),
               x = x_value,
               y = y_value,
               color = colour_value
  )
  p <- plotly::layout(p,
              xaxis = list(title = x_title),
              yaxis = list(title = y_title))
  p
})

```

***

Plot description:

Sequencing is called *saturated* when generating more sequencing output from a cDNA library does not substantially increase the number of detected features in a sample. Since the number of detected features can act as a technical confounder, and thereby drive substructure in the data, it is advisable to aim for a saturated sequencing by either adding more sequencing output or decreasing the number of samples until saturation is achieved. [@zhang_one_2018] gives advise on how to choose the optimal cell number given a fixed sequencing budget
