
### {{ title }}

<!-- Component created on {{ date }} -->

```{r}
{{ env_id }} = readRDS("envs/{{ env_id }}.rds")

is_shiny <- identical(knitr::opts_knit$get("rmarkdown.runtime"), "shiny")
```

```{r, eval=!is_shiny}

x_value <- {{ env_id }}$x[[1]]
x_title <- names({{ env_id }}$x[1])

y_value <- {{ env_id }}$y[[1]]
y_title <- names({{ env_id }}$y[1])

if(!is.null({{ env_id }}$colour_by)) {
  colour_value <- {{ env_id }}$colour_by[[1]]
  df <- data.frame({{ env_id }}$x, {{ env_id }}$y, {{ env_id }}$colour_by)
} else {
  df <- data.frame({{ env_id }}$x, {{ env_id }}$y)
}

# devtools::install_github('yihui/xfun')
# embed_file() requires a few more packages
xfun::pkg_load2(c('base64enc', 'htmltools', 'mime'))

embed_var = function(x, ...) {
  f = tempfile(fileext = '.csv')
  write.csv(x, f)
  xfun::embed_file(f, text = 'Download full data as .csv', ...)
}
# download_link
embed_var(df)

p <- plotly::plot_ly(data.frame(x_value, y_value, colour_value = I("black")),
             x = x_value,
             y = y_value,
             color = colour_value
)
p <- plotly::layout(p,
            xaxis = list(title = x_title),
            yaxis = list(title = y_title))
p

```

```{r, eval=is_shiny}

ui_list <- list()

# devtools::install_github('yihui/xfun')
# embed_file() requires a few more packages
xfun::pkg_load2(c('base64enc', 'htmltools', 'mime'))

embed_var = function(x, ...) {
  f = tempfile(fileext = '.csv')
  write.csv(x, f)
  xfun::embed_file(f, text = 'Download full data as .csv', ...)
}


# selection field for x
if ({{ env_id }}$x_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_x_{{ env_id }}", label = "Select data for x axis:",
              choices = names({{ env_id }}$x)))
}

# selection field for y
if ({{ env_id }}$y_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_y_{{ env_id }}", label = "Select data for y axis:",
              choices = names({{ env_id }}$y)))
}

# selection field for colour_by
if ({{ env_id }}$colour_by_selection){
  ui_list <- rlist::list.append(ui_list,
  selectInput("select_colour_{{ env_id }}", label = "Select colouring:",
              choices = names({{ env_id }}$colour_by)))
}

# Checkbox and selection field for colour by sample name
if (!is.null({{ env_id }}$labels)) {
  ui_list <- rlist::list.append(ui_list,
                                tags$div(checkboxInput("checkbox_{{ env_id }}", label = "Colour by sample name", value = FALSE),
                                        selectInput("select_name_{{ env_id }}", label = NULL, choices = {{ env_id }}$labels)
  ))
}

# Create data.frame for download
df_list <- list()
if (!is.null({{ env_id }}$labels)) df_list <- rlist::list.append(df_list, {{ env_id }}$labels)
df_list <- rlist::list.append(df_list, c({{ env_id }}$x, {{ env_id }}$y))
if (!is.null({{ env_id }}$colour_by)) df_list <- rlist::list.append(df_list, {{ env_id }}$colour_by)
df <- do.call("data.frame", df_list)

# download_link
ui_list <- rlist::list.append(ui_list, embed_var(df))

fillCol(flex = c(NA, 1),
        do.call("inputPanel", ui_list),
        plotly::plotlyOutput("plot_{{ env_id }}", height = "100%")
        )

output$plot_{{ env_id }} <- plotly::renderPlotly({

  if (!{{ env_id }}$x_selection){
    x_value <- {{ env_id }}$x[[1]]
    x_title <- names({{ env_id }}$x[1])
    x <- {{ env_id }}$x[1]
  } else {
    x_value <- {{ env_id }}$x[[input$select_x_{{ env_id }}]]
    x_title <- input$select_x_{{ env_id }}
    x <- {{ env_id }}$x[input$select_x_{{ env_id }}]
  }

  if (!{{ env_id }}$y_selection){
    y_value <- {{ env_id }}$y[[1]]
    y_title <- names({{ env_id }}$y[1])
    y <- {{ env_id }}$y[1]
  } else {
    y_value <- {{ env_id }}$y[[input$select_y_{{ env_id }}]]
    y_title <- input$select_y_{{ env_id }}
    y <- {{ env_id }}$y[input$select_y_{{ env_id }}]
  }

  if (!{{ env_id }}$colour_by_selection){
    if (!is.null({{ env_id }}$colour_by)){
      colour_value <- {{ env_id }}$colour_by[[1]]
      colour <- {{ env_id }}$colour_by[1]
    } else {
      colour_value <- NULL
      }
  } else {
    colour_value <- {{ env_id }}$colour_by[[input$select_colour_{{ env_id }}]]
    colour <- {{ env_id }}$colour_by[input$select_colour_{{ env_id }}]
  }

  # create data.frame for plot
  plot_list <- list()
  if (!is.null({{ env_id }}$labels)) plot_list <- rlist::list.append(plot_list, {{ env_id }}$labels)
  plot_list <- rlist::list.append(plot_list, c(x, y))
  if (!is.null({{ env_id }}$colour_by)) plot_list <- rlist::list.append(plot_list, colour)
  plot_df <- do.call("data.frame", plot_list)
  
  a <- NULL
  labels <- NULL
  
  if (!is.null({{ env_id }}$labels)) {
    if (input$checkbox_{{ env_id }}) {
      colour_value <- NULL
      point_index <- match(input$select_name_{{ env_id }}, plot_df[[1]])
      point <- plot_df[point_index,]
      a <- list(
        x = point[,2],
        y = point[,3],
        text = point[,1],
        xref = "x",
        yref = "y",
        showarrow = T,
        arrowhead = 7,
        arrowcolor = "red",
        ax = 20,
        ay = -40
      )
    }
  }
  
  if (!is.null({{ env_id }}$labels)) labels <- plot_df[[1]]
  
  p <- plotly::plot_ly(plot_df,
               x = x_value,
               y = y_value,
               color = colour_value,
               text = labels
  )
  p <- plotly::add_markers(p)
  p <- plotly::layout(p,
              xaxis = list(title = x_title),
              yaxis = list(title = y_title),
              annotations = a)
  p
})

```

***

Plot description:

Sequencing is called *saturated* when generating more sequencing output from a cDNA library does not substantially increase the number of detected features in a sample. Since the number of detected features can act as a technical confounder, and thereby drive substructure in the data, it is advisable to aim for a saturated sequencing by either adding more sequencing output or decreasing the number of samples until saturation is achieved. [@zhang_one_2018] gives advise on how to choose the optimal cell number given a fixed sequencing budget


